### 2015-01-13 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added figures and other content to report

@@

\subsection{Construction}
\label{sec:Construction}
Two structures, shown in Fig.~\ref{fig:struct_pics}, were used for the experiments. Each structure contained a ground level floor composed of concrete walls. The West Structure contained a second level.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/east_structure}
\\~\\
\includegraphics[width=6in]{../../Figures/west_structure}
\caption{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_2nd_Floor_Metric_Simple}
\caption{West Structure first floor (top) and second floor (bottom) layouts.}
\label{fig:west_general_plan}
\end{figure}

\clearpage
\section{Fuel Load}

\section{Instrumentation}

\section{Uncertainty}

\section{Experimental Procedure}

\subsection{Tests 18 and 19}
Tests 18 and 19 varied in that the first floor south side door was open for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 18. Both double doors and the south side door were open on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:test_18_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 19. Both double doors were open and the south side door was closed on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:test_19_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014BDP_A10_8_All_Streams}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_All_Streams}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_West_063014_SS_BDP_A10}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014BDP_A10_8_CW_vs_CCW}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_CW_vs_CCW}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_West_063014_SS_BDP_A10}
\end{figure}

>>>>

\section{Background}
\label{sec:Background}

\subsection{Hose Stream Patterns}
\label{sec:Hose_Stream_Patterns}

\subsection{Application Patterns}
\label{Application_Patterns}

@@

\subsection{Construction}
\label{sec:Construction}
Two structures, shown in Fig.~\ref{fig:struct_pics}, were constructed for the experiments. Each structure contained a ground level floor composed of concrete walls. The West Structure contained a second level.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/east_structure}
\\~\\
\includegraphics[width=6in]{../../Figures/west_structure}
\caption[East and West Test Structures]{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_2nd_Floor_Metric_Simple}
\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts.}
\label{fig:west_general_plan}
\end{figure}

\section{Fuel Load}
\label{sec:Fuel_Load}

\section{Instrumentation}
\label{sec:Instrumentation}

\section{Uncertainty}
\label{sec:Uncertainty}

\section{Experimental Procedure}
\label{sec:Experimental_Procedure}

\subsection{Hose Stream Pattern Experiments}
\label{sec:Hose_Stream_Pattern_Experiments}

\subsection{Application Pattern Experiments}
\label{Application_Pattern_Experiments}

Two sets of experiments involving application patterns, Tests 18 and 19, were conducted. The two sets varied in that the first floor south side door was open for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure first and second floor layouts for Test 18]{West Structure first floor (top) and second floor (bottom) layouts for Test 18. Both double doors and the south side door were open on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:test_18_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19. Both double doors were open and the south side door was closed on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:test_19_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
\caption{Average Velocity of Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
\caption{Average Velocity of Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of North Double Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of North Double Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
\end{figure}
